DESIGNATION_DRAFT

### 2021-08-30 R/DESIGNATION_DRAFT.Rmd
On the way of Bonus correction

if (scenario == "RIL3fuelhollow"| (scenario == "manual"& fuel =="2")){VO = objective #3604 rows
}else{
  VO = (objective + (objective*((advancedloggingparameters$ObjectiveBonus)/100))) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
}

(20 + (20*0.3))*6.25
(20*6.25) + ((20*6.25)*0.3) #same

>>>>

if (fuel =="2"){
  VO = objective * unique(inventory$PlotArea)
}else{
  VO = (objective +
          (objective *((advancedloggingparameters$ObjectiveBonus)/100))
        ) * unique(inventory$PlotArea) # to compensate for the designated hollow wood.
}

(20 + (20*0.3)) *6.25
(20*6.25) + ((20*6.25)*0.3) #same
